---
title: "Non-glucophily and metabolic strategies"
output: html_notebook
---

Do we see an enrichment for non-glucophilic traits in generalists or specialists
```{r Nonglucophily analyses with generalists and specialists, message = FALSE, insert = FALSE, warning= FALSE}

SugarData_df = unique(data.frame(Sugar_df[,c(1:3)]))
SugarData_df$NonGlucophilic = rep("Glucophilic", nrow(SugarData_df))
NONGLUCO = Nonglucophily[which(Nonglucophily$Non.glucophily >= 1), "Strain"]
SugarData_df[which(SugarData_df$PU %in% NONGLUCO), "NonGlucophilic"] = "Non-glucophilic"
SugarData_df$Strategy = rep("Normal", nrow(SugarData_df))
SugarData_df[which(SugarData_df$PU %in% Generalist_df$Strain), "Strategy"] = "Generalist"
SugarData_df[which(SugarData_df$PU %in% Specialist_df$Strain), "Strategy"] = "Specialist"

STRATEGY = unique(SugarData_df$Strategy)
NONGLUCOPHILY = unique(SugarData_df$NonGlucophilic)

NonGluco_Strategy_df = data.frame(Strategy = character(), 
                                  Glucophily = character(),
                                  Count = numeric(), 
                                  Proportion = numeric())
k = 1
for(i in 1:length(STRATEGY)){
  TEMP = SugarData_df[which(SugarData_df$Strategy == STRATEGY[[i]]),]
  for(j in 1:length(NONGLUCOPHILY)){
    NONGLUCTEMP = length(which(TEMP$NonGlucophilic == NONGLUCOPHILY[[j]]))
    NonGluco_Strategy_df[k, 1] = STRATEGY[[i]]
    NonGluco_Strategy_df[k, 2] = NONGLUCOPHILY[[j]]
    NonGluco_Strategy_df[k, 3] = NONGLUCTEMP
    NonGluco_Strategy_df[k, 4] = NONGLUCTEMP/nrow(TEMP)
    k = k+1
    
  }
}


a = ggplot(NonGluco_Strategy_df, aes(x = Strategy, y = Proportion, group = Glucophily, fill = factor(Glucophily)))
a = a + geom_bar(stat = "identity", color = "black")
a = a + scale_fill_manual(values = c("white", "gray40"), name = "Glucophily")
a = a + scale_y_continuous(expand = c(0, 0))
a = a + theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line.x = element_line(color = "black"), 
              axis.line.y = element_line(color = "black"),
              axis.text.x = element_text(size = 9, color = "black", vjust = 0.2),
              legend.title = element_text(face = "bold"), 
              axis.title = element_text(face = "bold"), 
              strip.background = element_rect(fill = "white"), 
              strip.text = element_text(face = "bold", size = 10),
              )
a = a + xlab("Glucophily") + ylab("Proportion")
ggsave("Non-glucophily_MetabolicStrategy.pdf")
ggsave("Non-glucophily_MetabolicStrategy.png")



BRNONGLUPRES = nrow(Generalist_df[which(Generalist_df$Strain %in% Nonglucophily$Strain),])
BRGLUPRES = nrow(Generalist_df[-which(Generalist_df$Strain %in% Nonglucophily$Strain),])
CLADENONGLUPRE =  nrow(Sugar_m[which(Sugar_m$PU %in% Nonglucophily$Strain),])-nrow(Generalist_df)
CLADEGLUPRE = nrow(Sugar_m[-which(Sugar_m$PU %in% Nonglucophily$Strain),])- nrow(Generalist_df)

TEMP_M = matrix(0, nrow = 2, ncol = 2)
TEMP_M[1,1] = BRNONGLUPRES
TEMP_M[1,2] = CLADENONGLUPRE
TEMP_M[2,1] = BRGLUPRES
TEMP_M[2,2] = CLADEGLUPRE
TEMPTEST = fisher.test(TEMP_M, alternative = "great")  
NonGlucophily_GenSpec_df = matrix(0, nrow = 2, ncol = 8)
NonGlucophily_GenSpec_df = data.frame(NonGlucophily_GenSpec_df)
colnames(NonGlucophily_GenSpec_df) = c("Type", "Classification", "Type_with", "Type_without", "Subphylum_with", "Subphylum_without", "Estimate", "pValue")

NonGlucophily_GenSpec_df[1,1] = "Breadth"
NonGlucophily_GenSpec_df[1,2] = "Generalist"
NonGlucophily_GenSpec_df[1,3] = BRNONGLUPRES
NonGlucophily_GenSpec_df[1,4] = BRGLUPRES
NonGlucophily_GenSpec_df[1,5] = CLADENONGLUPRE
NonGlucophily_GenSpec_df[1,6] = CLADEGLUPRE
NonGlucophily_GenSpec_df[1,7] = TEMPTEST$estimate
NonGlucophily_GenSpec_df[1,8] = TEMPTEST$p.value

#Specialist Breadth
BRNONGLUPRES = nrow(Specialist_df[which(Specialist_df$Strain %in% Nonglucophily$Strain),])
BRGLUPRES = nrow(Specialist_df[-which(Specialist_df$Strain %in% Nonglucophily$Strain),])
CLADENONGLUPRE =  nrow(Sugar_m[which(Sugar_m$PU %in% Nonglucophily$Strain),])-nrow(Specialist_df)
CLADEGLUPRE = nrow(Sugar_m[-which(Sugar_m$PU %in% Nonglucophily$Strain),])-nrow(Specialist_df)

TEMP_M = matrix(0, nrow = 2, ncol = 2)
TEMP_M[1,1] = BRNONGLUPRES
TEMP_M[1,2] = CLADENONGLUPRE
TEMP_M[2,1] = BRGLUPRES
TEMP_M[2,2] = CLADEGLUPRE
TEMPTEST = fisher.test(TEMP_M, alternative = "great")  

NonGlucophily_GenSpec_df[2,1] = "Breadth"
NonGlucophily_GenSpec_df[2,2] = "Specialist"
NonGlucophily_GenSpec_df[2,3] = BRNONGLUPRES
NonGlucophily_GenSpec_df[2,4] = BRGLUPRES
NonGlucophily_GenSpec_df[2,5] = CLADENONGLUPRE
NonGlucophily_GenSpec_df[2,6] = CLADEGLUPRE
NonGlucophily_GenSpec_df[2,7] = TEMPTEST$estimate
NonGlucophily_GenSpec_df[2,8] = TEMPTEST$p.value

NonGlucophily_GenSpec_df$P_adj = p.adjust(NonGlucophily_GenSpec_df$pValue, method = "BH")
NonGlucophily_GenSpec_df$Sig = rep("Not Significant", nrow(NonGlucophily_GenSpec_df))
NonGlucophily_GenSpec_df[which(NonGlucophily_GenSpec_df$P_adj <= 0.05),"Sig"] = "Significant"

SigNonGlucophily_GenSpec_df = NonGlucophily_GenSpec_df[which(NonGlucophily_GenSpec_df$Sig == "Significant"),]
NonGlucophily_GenSpec_df2 = SigNonGlucophily_GenSpec_df[,c(1:6)]
NonGlucophily_GenSpec_df2 = melt(NonGlucophily_GenSpec_df2)
NonGlucophily_GenSpec_df2$Proportion = rep(0, nrow(NonGlucophily_GenSpec_df2))

CLASS = unique(NonGlucophily_GenSpec_df2$Classification)
TYPE = unique(NonGlucophily_GenSpec_df2$Type)
for(i in 1:length(CLASS)){
  for(j in 1:length(TYPE)){
    TEMP = NonGlucophily_GenSpec_df2[which(NonGlucophily_GenSpec_df2$Type == TYPE[[j]] & NonGlucophily_GenSpec_df2$Classification == CLASS[[i]]),]
    VARIABLE = unique(TEMP$variable)
    for(v in 1:length(VARIABLE)){
      ROW = which(NonGlucophily_GenSpec_df2$variable == VARIABLE[[v]] & NonGlucophily_GenSpec_df2$Type == TYPE[[j]] & NonGlucophily_GenSpec_df2$Classification == CLASS[[i]])
     
       if(VARIABLE[[v]] == "Type_with"){
        NonGlucophily_GenSpec_df2[ROW,"Proprtion"] = TEMP[which(TEMP$variable == "Type_with"), "value"]/sum(TEMP[which(TEMP$variable == "Type_with"), "value"], TEMP[which(TEMP$variable == "Type_without"), "value"])
        
      }else if(VARIABLE[[v]] == "Type_without"){
                NonGlucophily_GenSpec_df2[ROW,"Proprtion"] = TEMP[which(TEMP$variable == "Type_without"), "value"]/sum(TEMP[which(TEMP$variable == "Type_with"), "value"], TEMP[which(TEMP$variable == "Type_without"), "value"])
                
      }else if(VARIABLE[[v]] == "Subphylum_with"){
                NonGlucophily_GenSpec_df2[ROW,"Proprtion"] = TEMP[which(TEMP$variable == "Subphylum_with"), "value"]/sum(TEMP[which(TEMP$variable == "Subphylum_with"), "value"], TEMP[which(TEMP$variable == "Subphylum_without"), "value"])
                
      }else{
         NonGlucophily_GenSpec_df2[ROW,"Proprtion"] = TEMP[which(TEMP$variable == "Subphylum_without"), "value"]/sum(TEMP[which(TEMP$variable == "Subphylum_with"), "value"], TEMP[which(TEMP$variable == "Subphylum_without"), "value"])

      }
    }
  }
}
NonGlucophily_GenSpec_df2$Clade = rep("Subphylum", nrow(NonGlucophily_GenSpec_df2))
NonGlucophily_GenSpec_df2[which(NonGlucophily_GenSpec_df2$variable %in% c("Type_with", "Type_without")), "Clade"] = "Generalist"

NonGlucophily_GenSpec_df2[which(NonGlucophily_GenSpec_df2$variable %in% c("Type_with", "Subphylum_with")), "Variable"] = "With"
NonGlucophily_GenSpec_df2[which(NonGlucophily_GenSpec_df2$variable %in% c("Type_without", "Subphylum_without")), "Variable"] = "Without"


a = ggplot(NonGlucophily_GenSpec_df2, aes(x = Clade, y = Proprtion, fill = Variable, group = Classification))
a = a + geom_bar(stat = "identity", position = "fill", colour = "black")
a = a + facet_wrap(.~Type)
a = a + scale_fill_manual(values = c("#19567C", "gray80"), name = "Class")
a = a + scale_y_discrete(expand = c(0, 0))
a = a + theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line.x = element_line(color = "black"), 
              axis.line.y = element_line(color = "black"),
              axis.text.x = element_text(size = 8, vjust = 0.2,color = "black"),
              strip.background = element_rect(colour="white", fill= "white"), 
              strip.text.x = element_text(face = "bold"), 
              axis.title.y = element_blank(), 
              axis.title.x = element_blank(), 
              axis.ticks.x = element_blank(), 
              legend.title = element_text(face = "bold"),
              axis.text = element_blank(), 
              axis.ticks = element_blank()
              )
a
ggsave("Nonglucophily_mosaic_NotCorr.pdf")
ggsave("Nonglucophily_mosaic_NotCorr.png")


```


Specialists were not associated with non-glucophily for breadth. To limit the number of tests we will be doing, we will only be looking at specific sugar nonglucophily associated with generalists and not specialists. 
```{r Nonglucophily for specific sugars generalists and specialists}
SUGARS = colnames(Nonglucophilic_all)[4:ncol(Nonglucophilic_all)]

#### Breadth Generalists and Specialists with specific sugar non-glucophily
#Generalist
Gen_SugarNonGluco_Breadth_df = data.frame(Sugar = character(), 
                                          Type_with = numeric(),
                                          Type_without = numeric(),
                                          Subphylum_with = numeric(),
                                          Suphylum_without = numeric(),
                                          Prop_Type_w = numeric(),
                                          Prop_Type_wo = numeric(),
                                          Prop_Sub_w = numeric(),
                                          Prop_Sub_wo = numeric(),
                                          Estimate = numeric(),
                                          p_value = numeric())
SUGARS = Sugar
for(i in 1:length(SUGARS)){
  SUGARCOL = which(colnames(Nonglucophilic_all) == SUGARS[[i]])
  TEMPSUGAR = Nonglucophilic_all[which(Nonglucophilic_all[,SUGARCOL] == 1), "PU"]
  BRNONGLUPRES = nrow(Generalist_df[which(Generalist_df$Strain %in% TEMPSUGAR),])
  BRGLUPRES = nrow(Generalist_df[-which(Generalist_df$Strain %in% TEMPSUGAR),])
  CLADENONGLUPRE =  nrow(Sugar_m[which(Sugar_m$PU %in% TEMPSUGAR),])
  CLADEGLUPRE = nrow(Sugar_m[-which(Sugar_m$PU %in% TEMPSUGAR),])

  TEMP_M = matrix(0, nrow = 2, ncol = 2)
  TEMP_M[1,1] = BRNONGLUPRES
  TEMP_M[1,2] = CLADENONGLUPRE
  TEMP_M[2,1] = BRGLUPRES
  TEMP_M[2,2] = CLADEGLUPRE
  TEMPTEST = fisher.test(TEMP_M, alternative = "great") 
  Gen_SugarNonGluco_Breadth_df[i,1] = SUGARS[[i]]
  Gen_SugarNonGluco_Breadth_df[i,2] = BRNONGLUPRES
  Gen_SugarNonGluco_Breadth_df[i,3] = BRGLUPRES
  Gen_SugarNonGluco_Breadth_df[i,4] = CLADENONGLUPRE
  Gen_SugarNonGluco_Breadth_df[i,5] = CLADEGLUPRE
  Gen_SugarNonGluco_Breadth_df[i,6] = BRNONGLUPRES/(BRNONGLUPRES+BRGLUPRES)
  Gen_SugarNonGluco_Breadth_df[i,7] = BRGLUPRES/(BRNONGLUPRES+BRGLUPRES)
  Gen_SugarNonGluco_Breadth_df[i,8] = CLADENONGLUPRE/(CLADENONGLUPRE+CLADEGLUPRE)
  Gen_SugarNonGluco_Breadth_df[i,9] = CLADEGLUPRE/(CLADENONGLUPRE+CLADEGLUPRE)
  Gen_SugarNonGluco_Breadth_df[i,10] = TEMPTEST$estimate
  Gen_SugarNonGluco_Breadth_df[i,11] = TEMPTEST$p.value
}

Gen_SugarNonGluco_Breadth_df$Classification = rep("Generalist", nrow(Gen_SugarNonGluco_Breadth_df))
Gen_SugarNonGluco_Breadth_df$Padj = p.adjust(Gen_SugarNonGluco_Breadth_df$p_value, method = "BH")
Gen_SugarNonGluco_Breadth_df$Sig_adj = rep("Not Significant", nrow(Gen_SugarNonGluco_Breadth_df))
Gen_SugarNonGluco_Breadth_df[which(Gen_SugarNonGluco_Breadth_df$Padj <= 0.05), "Sig_adj"] = "Significant"
SigGen_SugarNonGluco_Breadth_df = Gen_SugarNonGluco_Breadth_df[which(Gen_SugarNonGluco_Breadth_df$Sig_adj == "Significant"),]
```


Do we see an enrichment for non-glucophilic traits in nitrogen generalists or specialists
```{r Nonglucophily analyses with generalists and specialists, message = FALSE, insert = FALSE, warning= FALSE}

BRNONGLUPRES = nrow(Nitrogen_Generalist_df[which(Nitrogen_Generalist_df$Strain %in% Nonglucophily$Strain),])
BRGLUPRES = nrow(Nitrogen_Generalist_df[-which(Nitrogen_Generalist_df$Strain %in% Nonglucophily$Strain),])
CLADENONGLUPRE =  nrow(Nitrogen_m[which(Nitrogen_m$PU %in% Nonglucophily$Strain),])-nrow(Nitrogen_Generalist_df)
CLADEGLUPRE = nrow(Nitrogen_m[-which(Nitrogen_m$PU %in% Nonglucophily$Strain),])- nrow(Nitrogen_Generalist_df)

TEMP_M = matrix(0, nrow = 2, ncol = 2)
TEMP_M[1,1] = BRNONGLUPRES
TEMP_M[1,2] = CLADENONGLUPRE
TEMP_M[2,1] = BRGLUPRES
TEMP_M[2,2] = CLADEGLUPRE
TEMPTEST = fisher.test(TEMP_M, alternative = "great")  
Nitrogen_NonGlucophily_GenSpec_df = matrix(0, nrow = 2, ncol = 8)
Nitrogen_NonGlucophily_GenSpec_df = data.frame(Nitrogen_NonGlucophily_GenSpec_df)
colnames(Nitrogen_NonGlucophily_GenSpec_df) = c("Type", "Classification", "Type_with", "Type_without", "Subphylum_with", "Subphylum_without", "Estimate", "pValue")

Nitrogen_NonGlucophily_GenSpec_df[1,1] = "Breadth"
Nitrogen_NonGlucophily_GenSpec_df[1,2] = "Generalist"
Nitrogen_NonGlucophily_GenSpec_df[1,3] = BRNONGLUPRES
Nitrogen_NonGlucophily_GenSpec_df[1,4] = BRGLUPRES
Nitrogen_NonGlucophily_GenSpec_df[1,5] = CLADENONGLUPRE
Nitrogen_NonGlucophily_GenSpec_df[1,6] = CLADEGLUPRE
Nitrogen_NonGlucophily_GenSpec_df[1,7] = TEMPTEST$estimate
Nitrogen_NonGlucophily_GenSpec_df[1,8] = TEMPTEST$p.value

#Specialist Breadth
BRNONGLUPRES = nrow(Nitrogen_Specialist_df[which(Nitrogen_Specialist_df$Strain %in% Nonglucophily$Strain),])
BRGLUPRES = nrow(Nitrogen_Specialist_df[-which(Nitrogen_Specialist_df$Strain %in% Nonglucophily$Strain),])
CLADENONGLUPRE =  nrow(Nitrogen_m[which(Nitrogen_m$PU %in% Nonglucophily$Strain),])-nrow(Nitrogen_Specialist_df)
CLADEGLUPRE = nrow(Nitrogen_m[-which(Nitrogen_m$PU %in% Nonglucophily$Strain),])-nrow(Nitrogen_Specialist_df)

TEMP_M = matrix(0, nrow = 2, ncol = 2)
TEMP_M[1,1] = BRNONGLUPRES
TEMP_M[1,2] = CLADENONGLUPRE
TEMP_M[2,1] = BRGLUPRES
TEMP_M[2,2] = CLADEGLUPRE
TEMPTEST = fisher.test(TEMP_M, alternative = "great")  

Nitrogen_NonGlucophily_GenSpec_df[2,1] = "Breadth"
Nitrogen_NonGlucophily_GenSpec_df[2,2] = "Specialist"
Nitrogen_NonGlucophily_GenSpec_df[2,3] = BRNONGLUPRES
Nitrogen_NonGlucophily_GenSpec_df[2,4] = BRGLUPRES
Nitrogen_NonGlucophily_GenSpec_df[2,5] = CLADENONGLUPRE
Nitrogen_NonGlucophily_GenSpec_df[2,6] = CLADEGLUPRE
Nitrogen_NonGlucophily_GenSpec_df[2,7] = TEMPTEST$estimate
Nitrogen_NonGlucophily_GenSpec_df[2,8] = TEMPTEST$p.value

Nitrogen_NonGlucophily_GenSpec_df$P_adj = p.adjust(Nitrogen_NonGlucophily_GenSpec_df$pValue, method = "BH")
Nitrogen_NonGlucophily_GenSpec_df$Sig = rep("Not Significant", nrow(Nitrogen_NonGlucophily_GenSpec_df))
Nitrogen_NonGlucophily_GenSpec_df[which(Nitrogen_NonGlucophily_GenSpec_df$P_adj <= 0.05),"Sig"] = "Significant"

Sig_NitogenNonGlucophily_GenSpec_df = Nitrogen_NonGlucophily_GenSpec_df[which(Nitrogen_NonGlucophily_GenSpec_df$Sig == "Significant"),]
Nitrogen_NonGlucophily_GenSpec_df2 = Sig_NitogenNonGlucophily_GenSpec_df[,c(1:6)]
Nitrogen_NonGlucophily_GenSpec_df2 = melt(Nitrogen_NonGlucophily_GenSpec_df2)
Nitrogen_NonGlucophily_GenSpec_df2$Proportion = rep(0, nrow(Nitrogen_NonGlucophily_GenSpec_df2))

CLASS = unique(Nitrogen_NonGlucophily_GenSpec_df2$Classification)
TYPE = unique(Nitrogen_NonGlucophily_GenSpec_df2$Type)
for(i in 1:length(CLASS)){
  for(j in 1:length(TYPE)){
    TEMP = Nitrogen_NonGlucophily_GenSpec_df2[which(Nitrogen_NonGlucophily_GenSpec_df2$Type == TYPE[[j]] & Nitrogen_NonGlucophily_GenSpec_df2$Classification == CLASS[[i]]),]
    VARIABLE = unique(TEMP$variable)
    for(v in 1:length(VARIABLE)){
      ROW = which(Nitrogen_NonGlucophily_GenSpec_df2$variable == VARIABLE[[v]] & Nitrogen_NonGlucophily_GenSpec_df2$Type == TYPE[[j]] & Nitrogen_NonGlucophily_GenSpec_df2$Classification == CLASS[[i]])
     
       if(VARIABLE[[v]] == "Type_with"){
        Nitrogen_NonGlucophily_GenSpec_df2[ROW,"Proprtion"] = TEMP[which(TEMP$variable == "Type_with"), "value"]/sum(TEMP[which(TEMP$variable == "Type_with"), "value"], TEMP[which(TEMP$variable == "Type_without"), "value"])
        
      }else if(VARIABLE[[v]] == "Type_without"){
                Nitrogen_NonGlucophily_GenSpec_df2[ROW,"Proprtion"] = TEMP[which(TEMP$variable == "Type_without"), "value"]/sum(TEMP[which(TEMP$variable == "Type_with"), "value"], TEMP[which(TEMP$variable == "Type_without"), "value"])
                
      }else if(VARIABLE[[v]] == "Subphylum_with"){
                Nitrogen_NonGlucophily_GenSpec_df2[ROW,"Proprtion"] = TEMP[which(TEMP$variable == "Subphylum_with"), "value"]/sum(TEMP[which(TEMP$variable == "Subphylum_with"), "value"], TEMP[which(TEMP$variable == "Subphylum_without"), "value"])
                
      }else{
         Nitrogen_NonGlucophily_GenSpec_df2[ROW,"Proprtion"] = TEMP[which(TEMP$variable == "Subphylum_without"), "value"]/sum(TEMP[which(TEMP$variable == "Subphylum_with"), "value"], TEMP[which(TEMP$variable == "Subphylum_without"), "value"])

      }
    }
  }
}
Nitrogen_NonGlucophily_GenSpec_df2$Clade = rep("Subphylum", nrow(Nitrogen_NonGlucophily_GenSpec_df2))
Nitrogen_NonGlucophily_GenSpec_df2[which(Nitrogen_NonGlucophily_GenSpec_df2$variable %in% c("Type_with", "Type_without")), "Clade"] = "Generalist"

Nitrogen_NonGlucophily_GenSpec_df2[which(Nitrogen_NonGlucophily_GenSpec_df2$variable %in% c("Type_with", "Subphylum_with")), "Variable"] = "With"
Nitrogen_NonGlucophily_GenSpec_df2[which(Nitrogen_NonGlucophily_GenSpec_df2$variable %in% c("Type_without", "Subphylum_without")), "Variable"] = "Without"


a = ggplot(Nitrogen_NonGlucophily_GenSpec_df2, aes(x = Clade, y = Proprtion, fill = Variable))
a = a + geom_bar(stat = "identity", position = "fill", colour = "black")
a = a + facet_wrap(.~Type)
a = a + scale_fill_manual(values = c("#19567C", "gray80"), name = "Class")
a = a + scale_y_discrete(expand = c(0, 0))
a = a + theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line.x = element_line(color = "black"), 
              axis.line.y = element_line(color = "black"),
              axis.text.x = element_text(size = 8, vjust = 0.2,color = "black"),
              strip.background = element_rect(colour="white", fill= "white"), 
              strip.text.x = element_text(face = "bold"), 
              axis.title.y = element_blank(), 
              axis.title.x = element_blank(), 
              axis.ticks.x = element_blank(), 
              legend.title = element_text(face = "bold"),
              axis.text = element_blank(), 
              axis.ticks = element_blank()
              )
a
ggsave("Nitrogen_Nonglucophily_mosaic_NotCorr.pdf")
ggsave("Nitrogen_Nonglucophily_mosaic_NotCorr.png")


```

Specialists were not associated with non-glucophily for breadth. To limit the number of tests we will be doing, we will only be looking at specific sugar nonglucophily associated with generalists and not specialists. 
```{r Nonglucophily for specific sugars generalists and specialists}

#### Breadth Generalists and Specialists with specific sugar non-glucophily
#Generalist
Gen_NitrogenNonGluco_Breadth_df = data.frame(Nitrogen = character(), 
                                          Type_with = numeric(),
                                          Type_without = numeric(),
                                          Subphylum_with = numeric(),
                                          Suphylum_without = numeric(),
                                          Prop_Type_w = numeric(),
                                          Prop_Type_wo = numeric(),
                                          Prop_Sub_w = numeric(),
                                          Prop_Sub_wo = numeric(),
                                          Estimate = numeric(),
                                          p_value = numeric())
NITROGENS = Nitrogen
for(i in 1:length(SUGARS)){
  SUGARCOL = which(colnames(Nonglucophilic_all) == SUGARS[[i]])
  TEMPSUGAR = Nonglucophilic_all[which(Nonglucophilic_all[,SUGARCOL] == 1), "PU"]
  BRNONGLUPRES = nrow(Nitrogen_Generalist_df[which(Nitrogen_Generalist_df$Strain %in% TEMPSUGAR),])
  BRGLUPRES = nrow(Nitrogen_Generalist_df[-which(Nitrogen_Generalist_df$Strain %in% TEMPSUGAR),])
  CLADENONGLUPRE =  nrow(Nitrogen_m[which(Nitrogen_m$PU %in% TEMPSUGAR),])
  CLADEGLUPRE = nrow(Nitrogen_m[-which(Nitrogen_m$PU %in% TEMPSUGAR),])

  TEMP_M = matrix(0, nrow = 2, ncol = 2)
  TEMP_M[1,1] = BRNONGLUPRES
  TEMP_M[1,2] = CLADENONGLUPRE
  TEMP_M[2,1] = BRGLUPRES
  TEMP_M[2,2] = CLADEGLUPRE
  TEMPTEST = fisher.test(TEMP_M, alternative = "great") 
  Gen_NitrogenNonGluco_Breadth_df[i,1] = SUGARS[[i]]
  Gen_NitrogenNonGluco_Breadth_df[i,2] = BRNONGLUPRES
  Gen_NitrogenNonGluco_Breadth_df[i,3] = BRGLUPRES
  Gen_NitrogenNonGluco_Breadth_df[i,4] = CLADENONGLUPRE
  Gen_NitrogenNonGluco_Breadth_df[i,5] = CLADEGLUPRE
  Gen_NitrogenNonGluco_Breadth_df[i,6] = BRNONGLUPRES/(BRNONGLUPRES+BRGLUPRES)
  Gen_NitrogenNonGluco_Breadth_df[i,7] = BRGLUPRES/(BRNONGLUPRES+BRGLUPRES)
  Gen_NitrogenNonGluco_Breadth_df[i,8] = CLADENONGLUPRE/(CLADENONGLUPRE+CLADEGLUPRE)
  Gen_NitrogenNonGluco_Breadth_df[i,9] = CLADEGLUPRE/(CLADENONGLUPRE+CLADEGLUPRE)
  Gen_NitrogenNonGluco_Breadth_df[i,10] = TEMPTEST$estimate
  Gen_NitrogenNonGluco_Breadth_df[i,11] = TEMPTEST$p.value
}

Gen_NitrogenNonGluco_Breadth_df$Classification = rep("Generalist", nrow(Gen_NitrogenNonGluco_Breadth_df))
Gen_NitrogenNonGluco_Breadth_df$Padj = p.adjust(Gen_NitrogenNonGluco_Breadth_df$p_value, method = "BH")
Gen_NitrogenNonGluco_Breadth_df$Sig_adj = rep("Not Significant", nrow(Gen_NitrogenNonGluco_Breadth_df))
Gen_NitrogenNonGluco_Breadth_df[which(Gen_NitrogenNonGluco_Breadth_df$Padj <= 0.05), "Sig_adj"] = "Significant"
SigGen_NitrogenNonGluco_Breadth_df = Gen_NitrogenNonGluco_Breadth_df[which(Gen_NitrogenNonGluco_Breadth_df$Sig_adj == "Significant"),]
```
